Remark on the hypothetical judgment

### 2015-08-01 paper.tex
cite nice van dalen paper

What is the proper explanation of intuitionistic hypothetical judgment, and
thence propositional implication? The answer to this question is not clearly
determinate from the writings of Brouwer and Heyting, since in their lifetimes
they propounded multiple (sometimes conflicting) explanations of the
hypothetical judgment. To my mind, the determination of an acceptable
explanation must be, then, an act of abduction and reconstruction, taking
into account its adequacy for the expression of the bar theorem and, more
generally, the development of an open-ended framework for transcendental
arguments in mathematics.

>>>>

What is the proper explanation of intuitionistic hypothetical judgment, and
thence propositional implication? The answer to this question is not clearly
determinate from the writings of Brouwer, Heyting and Kolmogorov, since in their
lifetimes they propounded multiple (sometimes conflicting) explanations of the
hypothetical judgment \cite{van-dalen:2004}. To my mind, the determination of an
acceptable explanation must be, then, an act of abduction and reconstruction,
taking into account its adequacy for the expression of the bar theorem and, more
generally, the development of an open-ended framework for transcendental
arguments in mathematics.
